---
title: "RMarkdown"
output:
  pdf_document:
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.showtext = TRUE)
library(showtext)
library(tidyverse)
library(nycflights13)
library(ggplot2)
library(DBI)
library(modelr)
library(charlatan)
library(stringr) 
```


Markdown **easy to use** format for writing reports. It resembles what you naturally write every time you compose an email. In fact, you may have already used markdown *without realizing it*. These websites all rely on markdown formatting

* [Github](www.github.com)
* [StackOverflow](www.stackoverflow.com)
* [Reddit](www.reddit.com)

## Including Freqpoly
```{r echo=FALSE}
diamonds %>% 
  filter(carat<3) %>% 
  ggplot(mapping = aes(x=carat,color=cut))+
  geom_freqpoly(binwidth=0.6)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
